Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
artist recognition paragraph improved

Data:
This set encompass $1402$ songs $20$ artists, mostly rock and pop of different 
subgenres. Some results were available regarding the artist recognition
task. Few details given to preserve anonymity.

Let us be clear, the clustering method proposed in this work is not
intended to perform well at artist recognition. An obvious fact is that
we lose all timbral information which would be useful. However, we can
imagine that some artist use more often some patterns than others.
Best accuracy reported\footnote{few details given to preserve anonymity} 
is around $54.5\%$. Our result is $23.4\%$. Random
is around $5\%$. The confusion matrix can be seen in Figure \ref{fig:conf_mat}.
Details of the experiment follow.

>>>>

We apply our codebook to the artist recognition task.
Our data set encompass $1402$ songs from $20$ artists, 
mostly rock and pop of different subgenres. Results exist in the
litterature for that set \cite{Ellis2007}. The best accuracy is
$59\%$, whereas using only chroma as a representation yields an
accuracy of $33\%$. The latter results is obtained through a
gaussian mixture model.

Once again, the clustering method proposed in this work is not
intended to perform well at artist recognition. An obvious fact is that
we lose all timbral information which would be useful. However, we can
imagine that some artist use more often some patterns than others.
Our accuracy result is $23.4\%$ while random
is around $5\%$. 
The confusion matrix can be seen in Figure \ref{fig:conf_mat}.
Details of the experiment follow.
